% vim:ts=4:sw=4
% Copyright (c) 2014 Casper Ti. Vector
% Public domain.
\begin{cabstract}
智能化是视频监控的必然趋势，而基于视频监控的人脸检测与识别技术是融合了模式识别、图像处理、计算机视觉等多学科的具有挑战性的课题。由于它提供了一种可靠、方便的身份鉴别途径，而且人脸包含了重要的生物信息，具有极高的利用价值，因此有着广泛的应用环境和广阔的应用前景。然而，在监控视频当中，场景复杂多变、光照不受控制、图像质量低，这给人脸检测和识别带来了很大的挑战。本文在大量研究者工作的基础上，主要考虑监控场景下多姿态人脸的检测与识别问题。

针对监控环境下人脸形变、尺度、摄像头角度等问题，本文采用了一种基于级联可变形部件模型（DPM）的人脸检测方法。可变形部件模型有效地解决了因人脸姿态变化导致的漏检和因场景差异带来的误检，而级联机制有效的加快了检测速度。实验结果证明，该方法不但提高了对多人脸各个姿态的检测率，而且降低了人脸检测的误检率。并经过多线程和指令集优化后，在i5 CPU的PC上，对720p监控视频取得每秒25帧的速率。

针对人脸检测后的归一化问题，需要对多姿态的人脸进行特征点检测，也称人脸对齐。针对特征点问题当中的形变、遮挡及实时性的要求，本文提出了一种两级级联回归的人脸特征点定位方法，并通过自适应初始化的方式提高了定位的速度。方法采用了两级形状回归、局部坐标系下的形状索引特征和基于相关性的特征选择机制，实现了由粗到细的特征点定位。实验表明，该方法能够对多姿态的人脸实现精准的定位，且本文提出的自适应初始化的策略使得回归过程快速收敛，实现了人脸特征点的实时定位。

针对监控环境下人脸识别中人脸确认和辨识两个任务，本文提出了两级多任务度量学习方法用于人脸辨识，并通过简化的单任务度量学习方法应用于人脸确认任务。相比人脸确认这个二分类问题，人脸辨识问题可以被看作一个多分类问题。传统度量学习方法忽视了多分类问题当中共享的类间相似性，如：不同人的人脸有很强的视觉相似性。本文通过等价约束的方式学习一个度量矩阵。在第一级当中，采用了多种特征。在第二级当中，将每个人当作一个特定的子任务，而每个任务的标签信息代表着身份信息，最终通过多任务投票机制进行分类。该方法充分利用了成对的标签信息，并将该信息迁移到多分类任务当中。实验结果表明，该方法比传统多任务学习方法和多任务支持向量机有着更好的效果。
%传统的度量学习方法在应用于人脸识别时会产生过拟合、对图像噪声缺乏稳健性和训练速度慢等问题，且只针对从单一图像中一个特征学习马氏距离的度量，无法表达人脸图像的有效信息。
%针对监控环境下的人脸尺度、光照、形变复杂多变等特点，本文提出了一种基于两级多任务度量学习的人脸识别方法。
\end{cabstract}

\begin{eabstract}
%With the development of face detection and recognition technology, face recognition in video surveillance scenes has become a hot research topic for the growing demand of surveillance.
As intelligent video surveillance is an inevitable trend, face recognition in video surveillance scenes is a challenging task involving pattern recognition, image processing, computer vision and other subjects. Besides, it provides a reliable and convenient identity verification way and therefore has a wide range of application with broad prospects. However, the task becomes more difficult for the complex scenes, uncontrolled illumination and low resolution in video surveillance. Deep studies for face detection and face recognition in video surveillance scenes have been conducted, based on which the problem of face recognition in video surveillance is focused. In this paper, we mainly consider the pose-varied face detection and recognition problems.

In order to solve the problems such as human face pose, scale, camera angle and so on in video surveillance. This paper adopts cascaded Deformable part model (DPM) for face detection. The DPM model can effectively solve the miss detection and  false detection caused by pose variation and scenarios change. Experimental results show that the proposed method not only improves the accuracy of the multiple faces, but also reduces the false positive rate of face detection. And after the multi thread and instruction set optimization, the speed of face detection reaches at 25 frames per second for 720p video with an i5 CPU.

Aiming at the face normalization problem after face detection, a pose-varied face alignment is needed. In order to solve the problems of pose variation, occlusion and real time. A two level cascaded regression based method is proposed for facial landmark detection, and the adaptive restart mechanism boosts the speed of landmark detection. The method adopts two level shape regression which uses the local shape index feature and correlation based feature selection. Then, the face landmark detection is localized in a coarse to fine way. Experimental results show that the proposed method can be accurate and fast due to the adaptive restart mechanism for fast convergence, and it can be real time.

Aiming at the two tasks of face verification and face identification under video surveillance, a Two-level Multi-task Metric Learning (TMTL) method is presented for face identification. Then we use the simplified single task metric learning for face verification. Compare to the binary verification problem, the identification problem can be regarded as a multi classification problem. Traditional methods neglect the strong visual similarity between different classes, such as the different faces share strong visual similarity. Based on this, the Two-level Multi-task Metric Learning (TMTL) method is presented to learn a distance measure from equivalence constraints. Multiple features are adopted to represent the image information and learn the distance matrices in the first level. Then the task-specific learning paradigm and multi-task voting mechanism make full use of pairwise equivalence labels, which induces knowledge from anonymous pairs to multi-classification. Experimental results demonstrate that our method outperforms the recent multi-task learning approaches and multi-class support vector machine.
\end{eabstract}

