% vim:ts=4:sw=4
% Copyright (c) 2014 Casper Ti. Vector
% Public domain.
\chapter{攻读硕士学位期间的科研成果}

\section*{已发表论文}
    \begin{enumerate}
    \item Hong Liu, \textbf{Xuewu Zhang} and Pingping Wu. Two-level multi-task metric learning with application to multi-classification. \emph{IEEE International Conference on Image Processing (ICIP)}, pp. 2756-2760, September 27-30, Quebec, Canada, 2015. (EI, ISTP检索)
    \vspace{0.5em}
    \item Hong Liu, \textbf{Xuewu Zhang} and Pingping Wu. Regression based landmark estimation and multi-feature fusion for visual speech recognition. \emph{IEEE International Conference on Image Processing (ICIP)}, pp. 808-812, September 27-30, Quebec, Canada, 2015. (EI, ISTP检索)
    \vspace{0.5em}
    \item Pingping Wu, Hong Liu and \textbf{Xuewu Zhang}. Spontaneous versus posed smile recognition using discriminative local spatial-temporal descriptors. \emph{IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}, pp. 1249-1253, May 4-9, 2014, Florence, Italy. (EI，ISTP检索)
    \vspace{0.5em}
    \item Pingping Wu, Hong Liu*, Xiaofei Li, Ting Fan and \textbf{Xuewu Zhang}. A Novel Lip Descriptor for Audio-Visual Keyword Spotting Based on Adaptive Decision Fusion. \emph{IEEE Transactions on Multimedia (TMM)}, 18:3, pp. 326-338, 2016. (SCI检索, JCR二区).
    \vspace{0.5em}
    \item \textbf{张学武}, 吴平平, 刘宏. 基于视频序列的实时人脸性别识别[J]. \emph{华中科技大学学报}:自然科学版,41(S1):116-120,2013. (EI检索)
\end{enumerate}
\vspace{-1em}
\section*{已投稿论文}
    \begin{enumerate}
    \item Pingping Wu, Hong Liu*, \textbf{Xuewu Zhang} and Yuan Gao. How Do You Smile? Towards A Comprehensive Smile Analysis System. \textbf{Submitted} to NeuroComputing, 2016. (SCI检索)
    \vspace{0.5em}
    \item Pingping Wu，Hong Liu*, \textbf{Xuewu Zhang} and Yuan Gao. Spontaneous versus Posed Smile Recognition via Region-specific Texture Descriptor and Geometric Facial Dynamics.2016. \textbf{Submitted} to Frontiers of Information Technology and Electronic Engineering (SCI检索)
\end{enumerate}

\section*{参与项目}
    \begin{enumerate}
        \item 深圳市战略新兴产业项目：网络环境下的智能监控系统公共技术服务平台
        \item 深圳文化创意产业发展专项：机器人剧场-机器人演出关键技术及示范平台
        \item 科技部创新人才推进计划项目：面向复杂场景人机交互的嵌入式仿生视觉技术与系统
    \end{enumerate}
